---
title: "Data Exploratory"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
#### Data exploration on NBA dataset
```{r}
library(tidyverse)
library(DataExplorer)
```

#### Load data
```{r}
ranking = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/ranking.csv")
teams = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/teams.csv")
players = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/players.csv")
games = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/games.csv")
games_details = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/games_details.csv")
```
### Data overview
The dataframes we'll use are games_details, games, teams, players and ranking

### games_details
The most complete dataset from the five which game stats for each game and player.
```{r}
head(games_details,10)
```
#### Dimensions
The functions ```dim``` displays the dimension of the table and function ```glimpse```, from ```dplyr``` package, displays a vertical preview of the dataset.
```{r}
dim(games_details)
glimpse(games_details)
```
#### Values in detail
The mean and min-max values of the quantile variables

```{r}
games_stats <- games_details[c(10,11,13,14,16,17,19,21,22,23,24,25,26,27,28)]
summary(games_stats)
```

```Skim``` function from ```skimr``` package displays the same variable but also missing values, more quantile information and an inline histogram for each variable.
```{r}
library(skimr)
skim(games_details)
```
Metrics on data overall using funtion ```plot_intro```. 
```{r}
plot_intro(games_details)
```
#### Missing values
Check for missing values using function ```plot_missing```. We see that there isn’t a variable with such missing values that needs to be removed. In that case we should use the ```drop_columns``` function.
```{r}
plot_missing(games_details)
```

### games
```{r}
head(games,10)
```
#### Dimensions and columns
```{r}
dim(games)
glimpse(games)
```
#### Values in detail 
Analysis of quantile values
```{r}
games_pts <- games[c(8,9,10,12,13,15,16,17,18,19)]
summary(games_pts)
```
```{r}
skim(games_pts)
```
Metrics on data overall using funtion ```plot_intro```. 
```{r}
plot_intro(games)
```
#### Missing values
Check for missing values using function ```plot_missing```. We see that there isn’t a variable with such missing values that needs to be removed. In that case we should use the ```drop_columns``` function.
```{r}
plot_missing(games)
```

### ranking
```{r}
head(ranking,10)
```
#### Dimensions & columns
```{r}
dim(ranking)
glimpse(ranking)
```
#### Values in detail
```{r}
ranking_val <- ranking[c(7,8,9,10)]
summary(ranking_val)
```
```{r}
skim(ranking_val)
```
Metrics on data overall using funtion ```plot_intro```. 
```{r}
plot_intro(ranking)
```
#### Missing values
Check for missing values using function ```plot_missing```. We see that there isn’t a variable with such missing values that needs to be removed. In that case we should use the ```drop_columns``` function.
```{r}
plot_missing(ranking)
```

#### players
```{r}
head(players,10)
```

#### Dimensions
```{r}
dim(players)
glimpse(players)
```
```{r}
skim(players)
```

Metrics on data overall using funtion ```plot_intro```. 
```{r}
plot_intro(games)
```
#### Missing values
Check for missing values using function ```plot_missing```. We see that there isn’t a variable with such missing values that needs to be removed. In that case we should use the ```drop_columns``` function.
```{r}
plot_missing(games)
```

#### teams

```{r}
head(teams,10)
```
#### Dimensions
```{r}
dim(teams)
glimpse(teams)
```
#### Values in detail
```{r}
teams_stats <- teams[c(3,4,7,10)]
summary(teams_stats)
```
```{r}
skim(teams_stats)
```
Metrics on data overall using funtion ```plot_intro```. 
```{r}
plot_intro(teams)
```
#### Missing values
Check for missing values using function ```plot_missing```. We see that there isn’t a variable with such missing values that needs to be removed. In that case we should use the ```drop_columns``` function.
```{r}
plot_missing(teams_stats)
```







