---
title: "Data Exploration"
output: html_notebook
---
## Nba data analysis

Analyze the nba dataset following the steps below.

### Load the main packages
The main package ```tidyverse``` contains the ```ggplot``` and ```dplyr``` libraries which have our main functions.
```{r}
library(tidyverse)
```
### Load data
```{r}
ranking = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/ranking.csv")
teams = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/teams.csv")
player = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/players.csv")
games = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/games.csv")
games_details = read.csv("/Users/georgegasparis/GitHub/GraphBasketAnalysis/Data/games_details.csv")
```

### Overview
A quick dataset overview on the first 10 rows. The function ```head``` allows us to see the first 6 rows by default.
```{r}
head(games_details, 10)
```
### Dimensions
The functions ```dim``` displays the dimension of the table and function ```glimpse```, from ```dplyr``` package, displays a vertical preview of the dataset. 

```{r}
dim(games_details)
glimpse(games_details)
```
### Data summary
```Summary``` function shows each column, data type and other attributes. It's useful as we're dealing with a numeric dataset. For all the attributes it displays min, 1st quartile, median, mean, 3rd quartile and max values.
```{r}
summary(games_details)
```

```Skim``` function from ```skimr``` package displays the same variable but also missing values, more quantile information and an inline histogram for each variable.
```{r}
library(skimr)
skim(games_details)
```
### Data Profiling Report
Finally with the ```create_report``` function from the DataExplorer package, we get a full data profile of our data frame with just this one line of code. The function generate the "report.html" file which opens up in a browser tab. 
```{r}
library(DataExplorer)
DataExplorer::create_report(games_details)
```
Below we run the functions that are included in the report above which is only locally accessible.
First we can see the structure of the dataset with a quick
```{r}
plot_str(games_details)
```
Table visualization with lighting using the funtion ```plot_intro```
```{r}
plot_intro(games_details)
```
#### Missing values
Check for missing values using the function ```plot_missing```. We see that there isn't a variable with such missing values that needs to be removed. In that case we should use the ```drop_columns``` function.
```{r}
plot_missing(games_details)
```
#### Bar charts
To visualize frequency distributions for all discrete features using the ```plot_bar``` function.
```{r}
plot_bar(games_details)
```
#### Histograms
```{r}
plot_histogram(games_details)
```

















